R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-03-25 README.Rmd
readme
readme mentioning python

## This exampel reads text files but it will be updated to read NetCDF

@@

>>>>

>  This example reads text files but it will be updated to read NetCDF

@@

## Implementation in python:

I'm currently implementing a verison in python:

```{r, include=F}
data.frame(
  stringsAsFactors = FALSE,
                 R = c("fex","invfile",
                       "obs_addltime","obs_addstime","obs_addtime","obs_agg",
                       "obs_find_receptors","obs_footname","obs_format","obs_freq",
                       "obs_index","obs_invfiles","obs_list.dt","obs_meta",
                       "obs_out","obs_plot","obs_rbind","obs_read","obs_read_csvy",
                       "obs_read_nc","obs_roundtime","obs_summary",
                       "obs_table","obs_trunc","obs_write_csvy","plot.invfile",
                       "print.invfile","sr","summary.invfile"),
       description = c("File extension",
                       "Methods for objects with class 'invfile'",
                       "local hour (bsed on longitude and time)","Add solar time into obspack",
                       "Add times into obspack","Aggregates ObsPack by time",
                       "Compares expected receptors","Expected footprint name",
                       "Formatting data","return numeric vector in intervals",
                       "Summary of the ObsPack files (.txt)",
                       "Generate files to perform inverse modeling","list.dt","Read obspack metadata",
                       "outersect","Read obspack metadata","rbind obspack",
                       "Read obspack (.txt)","reads CSVY","Read obspack (.nc)",
                       "round seconds from \"POSIXct\" \"POSIXt\" classes",
                       "Summary of the ObsPack files (.txt)","Obspack Table",
                       "Trunc numbers with a desired number of decimals",
                       "Generates YAML and write data.frame",
                       "Methods for objects with class 'invfile'","Methods for objects with class 'invfile'",
                       "Extacts n last characters",
                       "Methods for objects with class 'invfile"),
            Python = c("","","","","","","","",
                       "","","OK","","","","","","","","","OK","",
                       "","","","","","","","")
) -> df

```{r, eval=TRUE, echo=FALSE}
knitr::kable(df)
